Algebraic Tori in Unitary Groups

### 2014-03-23 Paper.tex
minor changes

Finally, we must consider the group $H^1(\GalKbK,G)$. As $G$ is simply connect, this is only non-trivial at the real places of $K$.
In terms of real places, there are two cases to consider, when $E=\RR\times\RR$ then the $G$ is the automorphism group of a free module.
 As there are no forms of free modules, $H^1(\GalKbK,G)$ is then trivial. If $E=\C$, then $G$ is the automorphism group of a Hermitian space and $H^1(\GalKbK,G)$ classifies the Hermitian forms of the same discriminant as that defining $G$, over $\RR$ this means it classifies the signature.

Finally, we must consider the group $H^1(\GalKbK,G)$. As $G$ is simply connect, this is only non-trivial at the real places of $K$.
More concretely, as $\Gal(\C/\RR)$ has a single element, $H^1(\GalKbK,G)$ is determined by $g\in G$ such that $g\sigma(g) = 1$ modulo $hg\sigma(h^{-1})$.
TODO ---- do we actually want to explain this part concretely

>>>>

Finally, we must consider the group $H^1(\GalKbK,G)$. As $G$ is simply connect, this is only non-trivial at the real places of $K$.
In terms of real places, there are two cases to consider.
If $E=\C$, then $G$ is the automorphism group of a Hermitian space and $H^1(\GalKbK,G)$ classifies the Hermitian forms of the same discriminant as that defining $G$, as above, over $\RR$ this means it classifies the signature.
When $E=\RR\times\RR$ then the $G$ is the automorphism group of a free module.
 As there are no forms of free modules, $H^1(\GalKbK,G)$ is then trivial. 
TODO --- Find reference for this ----
